---
title: "Draft Quarto document"
author: "Your Name"
format: html
---

## Header 1

```{r setup}
library(tidyverse)
library(here)
library(fs)
source(here("R/functions.R"))
```

## Importing new data
```{r}
# here function: tells us where we are, while telling R to go back to where the project file is located - keeping your project contained
# new_data <- read_csv(here("data/new_data.csv"))

# here("data-raw/nurses-stress/stress/5C/5C_1586886626/HR.csv.gz") |>
#   read_csv(
#     show_col_types = FALSE,
#     name_repair = to_snake_case,
#     n_max = 100
#   )

# name_repair: updating column names while importing your data
# n_max: how many rows is loaded from this specific file
```

## Exercise: Reading other files

```{r}
#| eval: false #makes R not execute the code chunk
# read in a few other data files
here("data-raw/nurses-stress/stress/5C/5C_1586886712/HR.csv.gz") |>
  read_csv(
    show_col_types = FALSE,
    name_repair = to_snake_case
  )
```

## Making a function to add numbers
```{r}
#' Add two numbers together.
#'
#' @param num1 A number here.
#' @param num2 A number here.
#'
#' @returns Returns the sum of two numbers
#'
add_numbers <- function(num1, num2) {
  added <- num1 + num2
  return(added)
}

# {...} are used after function() to make a function body
# we don't necessarily need the return, but it can be good practice to make sure you get returned what you want
# to add roxygen comment; place cursor somewhere within your function
```

```{r}
# here used to be the read() function we generated, which is now in the R/functions.R
# be careful not to overwrite a function. Check if a function name is taken by looking up the potential help page: ?function
```

```{r}
here("data-raw/nurses-stress/stress/5C/5C_1586886626/HR.csv.gz") |>
  read()
```

```{r}
here("data-raw/nurses-stress/stress/5C/5C_1586886712/HR.csv.gz") |>
  read()
```


```{r}
# testing code exercise 16.7
# Outputs only 100 rows
here("data-raw/nurses-stress/stress/5C/5C_1586886712/HR.csv.gz") |>
  read()

# Outputs only 1000 rows
here("data-raw/nurses-stress/stress/5C/5C_1586886712/HR.csv.gz") |>
  read(max_rows = 1000)

# Outputs all rows (`Inf` means infinity)
here("data-raw/nurses-stress/stress/5C/5C_1586886712/HR.csv.gz") |>
  read(max_rows = Inf)
```


## Using map

```{r}
hr_files <- here("data-raw/nurses-stress/") |>
  dir_ls(regexp = "HR.csv.gz", recurse = TRUE)

# dir_ls lists all files in a folder
# regexp argument = lists all files related to "HR.csv.gz" in the folder
# recurse = TRUE, looks in all the folders within the root folder, which we listed (nurses-stress)

hr_data <- hr_files |>
  map(read) |> # NO BRACKETS!
  list_rbind(names_to = "file_path_id")

hr_data
```

Now, we'd like to add ID to the files and also combine the files into one file using combine rows - so we pipe to list_rbind() 

names_to = "file_path_id" since names are automatically lost


## 18.5 Exercise: Convert the map with reading code into a function and use on sleep

```{r}
read_all <- function(filename) {
  data <- here::here("data-raw/nurses-stress") |>
    fs::dir_ls(regexp = filename, recurse = TRUE) |>
    purrr::map(read) |> # NO BRACKETS!
    purrr::list_rbind(names_to = "file_path_id")
  return(data)
}

read_all("IBI.csv.gz")
```

## Exercise 19.2: Inspect and compare the data frames
```{r}
hr_data <- read_all("HR.csv.gz")

survey_data <- here("data-raw/nurses-stress/survey-results.csv.gz") |>
  read()

hr_data
survey_data

# date and time stamps are in different formats/columns in the two data sets
# number of rows and columns are not compatible - we would either need N/A values inserted or re-formatting
```

```{r}
hr_data |>
  mutate(
    id = str_extract(
      file_path_id,
      pattern = "/stress/[:alnum:]{2}/"
    ) |>
      str_remove("/stress/") |>
      str_remove("/"),
    .before = file_path_id
  ) |>
  select(-file_path_id)
```


## Exercise 19.7: Convert 'get ID' code into a function

```{r}
#' Extract participant ID from file_path_id
#'
#' @param data
#'
#' @returns data with ID
#'
get_participant_id <- function(data) {
  data_with_id <- data |>
    dplyr::mutate(
      id = stringr::str_extract(
        file_path_id,
        pattern = "/stress/[:alnum:]{2}/"
      ) |>
        stringr::str_remove("/stress/") |>
        stringr::str_remove("/"),
      .before = file_path_id
    ) |>
    dplyr::select(-file_path_id)

  return(data_with_id)
}

read_all("BVP.csv.gz")

read_all("BVP.csv.gz") |>
  get_participant_id()
```

## Exercise 19.8: Simplify the regex with look arounds
```{r}
get_participant_id_simple <- function(data) {
  data_with_id_simple <- data |>
    dplyr::mutate(
      id = stringr::str_extract(
        file_path_id,
        pattern = "(?<=/stress/)[:alnum:]{2}(?=/)"
      ),
      .before = file_path_id
    ) |>
    dplyr::select(-file_path_id)

  return(data_with_id_simple)
}

read_all("BVP.csv.gz") |> get_participant_id_simple()
```


## 20.3 Summarising with across
```{r}
hr_data <- read_all("HR.csv.gz") |>
  get_participant_id()

# applying more functions to the across function: give the across a list of functions as an argument
hr_data |>
  summarise(across(
    where(is.numeric),
    list(
      mean = mean,
      median = median,
      sd = sd
    )
  ))
```

Example of how to use as anonymous function (lambda function); providing several functions to a function - an unnamed function - we don't assign the function a name (object)
```{r}
# summarise(across(hr,\(x) mean(x, na.rm = TRUE)))

# but we don't have any N/As
# not a reusable function
# \(x) can also be replaced with function(x)
```


## 20.4 Working with dates
```{r}
hr_data |>
  mutate(
    datetime = lubridate::round_date(collection_datetime,
      unit = "minute"
    ),
    .before = collection_datetime
  )
```

## Summarising by groups
```{r}
hr_data |>
  mutate(
    collection_datetime = round_date(
      collection_datetime,
      unit = "minute"
    )
  ) |>
  summarise(
    across(
      where(is.numeric),
      list(
        mean = mean,
        sd = sd,
        median = median
      )
    ),
    .by = c(id, collection_datetime)
  )
```

## 20.6 Exercise: Convert the summarising code into a function
```{r}


```
